% THIS IS AN EXAMPLE DOCUMENT FOR VLDB 2012
% based on ACM SIGPROC-SP.TEX VERSION 2.7
% Modified by  Gerald Weber <gerald@cs.auckland.ac.nz>
% Removed the requirement to include *bbl file in here. (AhmetSacan, Sep2012)
% Fixed the equation on page 3 to prevent line overflow. (AhmetSacan, Sep2012)

\documentclass[sigconf]{acmart}

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
%\pagestyle{plain} % removes running headers

\usepackage{booktabs} % For formal tables

\usepackage{url}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{caption}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage[noend]{algpseudocode}
\usepackage{paralist}
\usepackage{listings}
\usepackage{fancyvrb}

\lstset{basicstyle=\ttfamily,
escapeinside={||},
mathescape=true}

%\newcommand\todo[1]{\textcolor{red}{#1}}
%\newcommand\srm[1]{}
\newcommand\srm[1]{\textcolor{red}{SAM:#1}}
\newcommand\ani[1]{\textcolor{blue}{ANI:#1}}


\newcommand{\todo}[1]{{\leavevmode\color{red}#1}}

\setcopyright{rightsretained}

%Conference
\acmConference[SIGMOD'18]{ACM SIGMOD/PODS International Conference on Management of Data}{June 2018}{Houston, Texas, U.S.A}
\acmYear{2018}
\copyrightyear{2018}

\begin{document}

\title{Analytics using GPU vs CPU: How different are they really?}

\begin{abstract}
There has been a significant excitement amount and recent work on gpu-based
database systems. Previous work have shown that these systems can perform an
order of magnitude better than cpu-based database system on analytical
workloads such as those found in data warehouses, decision support and business
intelligence applications. The elevator pitch behind this performance
difference is straightforward: gpu's have higher compute and memory bandwidth
than the cpu. 

A hardware guy would view this as hype. Given the general notion that database
operators are bandwidth-bound, one would expect the maximum gain would be the
ratio of the memory bandwidth of GPU to that of GPU. Also, given the
restrictive GPU programming model which requires running program over a large
number of threads, one would expect additional materializations leading to
further degradation in gain. In this paper, we demonstrate that both these
assumptions are false. We first show that join and sort achieve speedup larger
than the bandwidth ratio. Second, using known GPU optimization techniques, it
is possible to avoid the 'paradigm' tax. Finally, it is known that GPUs are
more expensive that CPU. We do a performance/cost analysis to show that GPUs
can be around 3x more cost-efficient when the critical section of the
computation fits in GPU memory.
\end{abstract}

\maketitle

\input{introduction}
\input{background}
\input{perop}
%\input{cost-modelling}

{
\bibliographystyle{ACM-Reference-Format}
\bibliography{bibs}  % vldb_sample.bib is the name of the Bibliography in this case
}

\input{appendix}

\end{document}

